\documentclass{tufte-handout}

\usepackage{fontspec}
\usepackage{ifxetex}

\setmainfont[Ligatures=TeX,Numbers=OldStyle]{AdellePE}

\ifxetex
  \newcommand{\textls}[2][5]{%
    \begingroup\addfontfeatures{LetterSpace=#1}#2\endgroup
  }
  \renewcommand{\allcapsspacing}[1]{\textls[15]{#1}}
  \renewcommand{\smallcapsspacing}[1]{\textls[10]{#1}}
  \renewcommand{\allcaps}[1]{\textls[15]{\MakeTextUppercase{#1}}}
  \renewcommand{\smallcaps}[1]{\smallcapsspacing{\scshape\MakeTextLowercase{#1}}}
  \renewcommand{\textsc}[1]{\smallcapsspacing{\textsmallcaps{#1}}}
\fi

\title{Questions}
\author{Rachael Carlson}
\date{\today}

\begin{document}
\maketitle

How did you get into teaching guitar?

How long have you been teaching guitar?

Did you have to start by teaching classical guitar?

Did you experience resistance in your offering of finger-style guitar?
\vspace{.15in}

\noindent How did you get your position at your university?

\vspace{.15in}

\noindent How many finger-style students do you have?
\vspace{.15in}

\noindent Do you think that it is necessary to have a performance and
recording career before a university of college will take one seriously as a
candidate for an instructor position?
\vspace{.15in}

\noindent As a finger-style guitarist teaching at a university what are your
thoughts on the current academic climate as it relates to guitar instruction
in the United States?
\vspace{.15in}

\noindent Are there other universities in the country that you are aware of
which offer finger-style guitar as a field of study?
\vspace{.15in}

\noindent Do you think that it is possible for a university to consider an
unsolicited application or proposal for a finger-style guitar program? If not,
how would you recommend that one pursue establishing a finger-style guitar program?
\vspace{.15in}

\noindent How was it for you when you first got your current job? Did you
experience resistance to your inclusion of finger-style guitar?
\vspace{.15in}

\noindent What are your thoughts, generally, about the presence of
finger-style guitar in a university? 

Do you think that it should be taught in a university setting?

Or, do you think that it would be better for finger-style guitar as a genre to
not be taught in a university setting?

\vspace{.15in}
\noindent I am hoping to get a job teaching finger-style guitar or guitar in
general at a university or college level. I will be completing my Master of
Music in finger-style guitar performance this May. I hope to complete an album
of music this summer. What recommendations would you have for me?

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
