\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\usepackage{xltxtra}
\defaultfontfeatures{Ligatures=Common,
Numbers=OldStyle,
Scale=MatchLowercase
}
\usepackage[backend=biber,isbn=false]{biblatex-chicago}
\addbibresource{references.bib}

\begin{document}
\noindent Rachael Carlson \hfill \today\\
\noindent Reading Response Week 13\\
\noindent Music 314\\

\noindent \fullcite{buhler2017}.\\

\noindent and\\

\noindent \fullcite{mccorkle}.\\

\begin{itemize}
\item What audience were they written for? Would these posts appeal to
  non-musicologists?
\item Do they convey a meaningful argument without further contextual
  understanding (i.e., knowledge of film music studies or the \emph{Star Wars}
  films)?
\end{itemize}

I believe that these articles were written for musicians, music-lovers, and
film-lovers. I do not think that these articles would appeal to
musicologists. I think that they are designed for non-musicologists. They both
read more like barely-below-surface level critiques of the use of music in a
major motion picture. It seams to me that \emph{Musicology Now} is attempting
to make itself relevant by having scholars write pithy articles on popular
topics. It is certainly pleasing that both scholars whom I read are actually
interested in film music in some manner. I half-expected to see that they were
scholars of Beethoven or some other such thing.

I have not seen \emph{Rogue One}. I was quite surprised that both articles
seemingly spoiled the end of the movie in their analysis of the music. While I
don't exactly care for the \emph{Star Wars} franchise, I was probably going to
watch \emph{Rogue One} at some point. I do think that I was able to gather
some information about the music even though I do not know anything about film
music studies. It is interesting that Buhler compared Williams to Holst and
McCorkle compared him Wagner. These are two completely different composers. I
would be interested to seem them debate the similarities and differences.

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
