\message{ !name(carlsonProgramNotes.tex)}\documentclass{article}
\usepackage[margin=1.5in]{geometry}
\usepackage{fontspec}
\usepackage[sf,bf]{titlesec}

\setmainfont{EB Garamond}
\setsansfont{Adobe Garamond Pro}
\begin{document}

\message{ !name(carlsonProgramNotes.tex) !offset(-3) }

\begin{center}
  Program\\
  Master's Recital in Finger-Style Guitar\\
  Rachael Carlson\\
  Greene Hall\\
  April 22, 2017, 7:30pm
\end{center}
\noindent Black Moon/Westward Move (2004)\dotfill Clive Carroll\\
6 min. \hfill (b. 1975)\\

\noindent Partita No. 3 in E Major: III. Gavotte en Rondeau (1720, 1736)\dotfill Johann Sebastian Bach\\
3 min. \hfill (1685 -- 1750)\\
\strut\hfill arranged by Rachael Carlson (b. 1988)\\

\noindent Watch the Tiger Walk (2016)\dotfill Rachael Carlson\\
5 min. \hfill (b. 1988)\\

\noindent Little Meggie (2001)\dotfill Michael Gulezian\\
5 min. \hfill (b. 1957)\\

\noindent Ants (unreleased)\dotfill Leo Kottke\\
6 min. \hfill (b. 1945)\\

\noindent The Staten Island Ferry (2017)\dotfill Rachael Carlson\\
3 min. \hfill (b. 1988)\\

\noindent Studio N. 5 (2011)\dotfill Pino Forastiere\\
5 min. \hfill (b. 1966)\\

\noindent Guitar Chimes (1929)\dotfill Arthur ``Blind'' Blake\\
3 min. \hfill (1896 -- 1934)\\

\noindent Six-String Suite: Eggtooth/Grim to the Brim/Orange Room (1982)\dotfill Leo Kottke\\
13 min. \hfill (b. 1945)\\

\noindent Madness (2013)\dotfill Matt Bellamy\\
5 min. \hfill (b. 1978)\\
\strut\hfill arranged by Luca Stricagnoli (b. 1991)\\

\noindent The Happy Couple (1981)\dotfill Michael Hedges\\
3 min. \hfill (1953 -- 1997)\\

\noindent Aerial Boundaries (1984)\dotfill Michael Hedges\\
5 min. \hfill (1953 -- 1997)\\
\clearpage

\section*{Program Notes}
\label{sec:program-notes}

\subsection*{``Black Moon''/``Westward Move'' by Clive Carroll}
\label{sec:black-moonw-move}

\subsection*{Partita No. 3 in E Major: III. Gavotte en Rondeau by Johann Sebastian Bach, arranged by Rachael Carlson}
\label{sec:partita-no.-3}

\subsection*{``Watch the Tiger Walk'' by Rachael Carlson}
\label{sec:watch-tiger-walk}

\subsection*{``Little Meggie'' by Rachael Carlson}
\label{sec:little-megg-rach}

\subsection*{``Ants'' by Leo Kottke}
\label{sec:ants-leo-kottke}

\subsection*{``The Staten Island Ferry'' by Rachael Carlson}

\subsection*{``Studio N. 5'' by Pino Forastiere}

\subsection*{``Guitar Chimes'' by Arthur ``Blind'' Blake}

\subsection*{Six-String Suite: ``Eggtooth''/``Grim to the Brim''/``Orange Room'' by Leo Kottke}

\subsection*{``Madness'' by Matt Bellamy, arranged by Luca Stricagnoli}

\subsection*{``The Happy Couple'' by Michael Hedges}

\subsection*{``Aerial Boundaries'' by Michael Hedges}


 \end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

\message{ !name(carlsonProgramNotes.tex) !offset(-97) }
